### 2014-05-26 tex/main-body-text.tex
Filled in results that were unclear/lacking

\subsection*{Analysis of coastal California steelhead} 
To compare the behavior of {\sc flock} to that of {\sc structure} we used a published 
dataset of 2596 steelhead \textit{Oncorhynchus mykiss}
genotyped at 15 microsatellite loci from \citet{Garzaetal_norcal}.  {\sc flock} was run six times using the default setting for all 
run parameters (initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0) for values of $K$ from 2 to 6. The stopping point of 
$K=6$ was chosen after four consecutive runs (at $K=6$) % <-- Patrick, is that right. were the non-plateau-ing runs at K=6?
yielded no plateau (see below). For each value of $K$ from 2 to 6, the no-admixture, 
uncorrelated-allele-frequency model implemented in {\sc structure} was run 6 times using 
50,000 sweeps of burn-in followed by 150,000 sweeps of sample collection from the posterior. 
All runs were performed on a (WHAT TYPE OF COMPUTER?) with an i7 3.40GHz processor and 8GB
of RAM. To facilitate the comparison of results from
the two programs, we derived $q_i$ values 
from {\sc flock}'s output by exponentiating the log-likelihood values for cluster membership  % <-- Patrick, please verify.
and rescaling so they summed to one.  These are then comparable to the $q_i$ values
returned by {\sc structure}, which, in the no-admixture case, are posterior probabilities of cluster membership.
The program {\sc clumpp} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program {\sc district} \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

\citet{Duc&Tur2012} promote a method for using {\sc flock} to estimate, $K$, the number of
subpopulations.  Their approach involves INSERT SHORT DESCRIPTION, INCLUDING DISCUSSION OF PLATEAUS.

@@

\begin{figure*}
\begin{center}
	% NOTE. Pat made Q-val-StrFloc.pdf that has all runs individually, replaced with 
	% all of them on same axis. It will look fine as a black and white with different 
	% characters.
 \includegraphics[width=\textwidth]{images/Figures-Pat/Qval-1plot.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{Fig.2}
\end{center}
\end{figure*}

>>>>

\subsection*{Analysis of coastal California steelhead} 
To compare the behavior of {\sc flock} to that of {\sc structure} we used a published 
dataset of 2596 steelhead \textit{Oncorhynchus mykiss}
genotyped at 15 microsatellite loci from \citet{Garzaetal_norcal}.  {\sc flock} was run six times using the default setting for all 
run parameters (initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0) for values of $K$ from 2 to 6. The stopping point of 
$K=6$ was chosen after four consecutive values of $K$
yielded no plateau (see below). For each value of $K$ from 2 to 6, the no-admixture, 
uncorrelated-allele-frequency model implemented in {\sc structure} was run 6 times using 
50,000 sweeps of burn-in followed by 150,000 sweeps of sample collection from the posterior. 
All runs were performed on a JNCS D685 with an i7 3.40GHz processor and 8GB
of RAM running 64-bit Windows 7 OS. For each run {\sc flock} reports the 
normalized likelihood values (the exponenetiated log-likelihood value for an individuals 
membership to each $K$ clusters scaled to sum to one). 
This value is comparable to the $q_i$ values
returned by {\sc structure}, which, in the no-admixture case, are posterior probabilities of cluster membership.
The program {\sc clumpp} \citep{Jak&Ros2007} was used to relabel clusters among different runs,
while the program {\sc district} \citep{Rosenberg2004} was used to plot individual \textit{$q_i$} values.

\citet{Duc&Tur2012} promote a method for using {\sc flock} to estimate, $K$, the number of
subpopulations. The user must first specify the number of runs (different initial allocation of individuals 
to each cluster) as well as the number of iterations individual has the chance to be reallocated 
to a different cluster. For each run the log-likelihood value of membership to all $K$ clusters is computed
and the difference between the cluster with the highest likelihood and second highest likelihood is reported (LLOD)
for each individual. Runs that converge on the same solution are indicated by the same mean LLOD score. and 
are referred to as a plateau. If for a given $k$ there may be multiple local maxima in addition to 
the global maximum, depending on the initial allocation of individuals the alorithm will result in finding
different plateaus. The plateau record is a list of how many runs ended up at these different solutions. 
\citet{Duc&Tur2012} developed two stopping rules that lead to the estimation of $K$. In the abscence of 
reasonable values for $k$ \citet{Duc&Tur2012} advocate running  {\sc flock} until either a single plateau 
$\geq$6 is reached or four consecutive $k$ values yield no plateaus. If the first stopping condition is satisfied,
the $K$ for which there is a a single plateau $\geq$6 is the point estimate for $K$. Alternatively, 
if multiple plateaus are observed with at least one plateau$\geq$6, the largest value of $K$ that satisfies 
this conditon should be taken as the lower bound estimate of $K$. If no plateaus \geq$6 are observed $K$
is \textit{undecided}.

@@

\begin{figure*}
\begin{center}
	% NOTE. Pat made Q-val-StrFloc.pdf that has all runs individually, replaced with 
	% all of them on same axis. It will look fine as a black and white with different 
	% characters.
 \includegraphics[width=\textwidth]{images/Figures-Pat/Qval-1plotGreyScale.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{Fig.2}
\end{center}
\end{figure*}
